\textls[-0]{\thetitle}

### 2023-03-15 metatheory-condensed.tex
typo?

We use universes à la \citet{coquand2013presheaf}, following \citet{kaposi2019gluing}.
Unlike Russell-style ones, these universes are not inhabited by types directly but rather by the \emph{codes} of types
and arguably behave better due to its closeness to Tarski-style universes~\cite{luo2012notes}. 
% and compatibility with our algebraic formulation of MLTT~\cite{coquand2018canonicity}. % I am not sure if I want this sentence or not
Term $\codety{T}$ encodes type~$T$ (\ruleref{tm/c}) and thus inhabits universe~$\cU$.
Type $\El{t}$ decodes term~$t$ (\ruleref{ty/el}).
%\footnote{By contrast,  Russel-style universes are inhabited by types directly.  Tarski-style universes are ``semantically more fundamental'' \cite{luo2012notes} and friendlier to our meta-theoretical reasoning.}
There is an infinite hierarchy of universes;
we omit universe levels in the presentation to avoid clutter.
%\rA{Why is W(t) a term and not a type?}\YZreply{I think the reviewer is wondering what is gained by encoding and decoding types, compared to types directly inhabiting universes.}

>>>>

We use universes à la \citet{coquand2013presheaf}, following \citet{kaposi2019gluing}.
Unlike Russell-style ones, these universes are not inhabited by types directly,
but rather by the \emph{codes} of types,
and arguably behave better due to its closeness to Tarski-style universes~\cite{luo2012notes}. 
% and compatibility with our algebraic formulation of MLTT~\cite{coquand2018canonicity}. % I am not sure if I want this sentence or not
Term $\codety{T}$ encodes type~$T$ (\ruleref{tm/c}) and thus inhabits universe~$\cU$.
Type $\El{t}$ decodes term~$t$ (\ruleref{ty/el}).
%\footnote{By contrast,  Russel-style universes are inhabited by types directly.  Tarski-style universes are ``semantically more fundamental'' \cite{luo2012notes} and friendlier to our meta-theoretical reasoning.}
There is an infinite hierarchy of universes;
we omit universe levels in the presentation to avoid clutter.
%\rA{Why is W(t) a term and not a type?}\YZreply{I think the reviewer is wondering what is gained by encoding and decoding types, compared to types directly inhabiting universes.}
